Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)

### 2025-05-22 cover_letter.qmd
Up title page

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
linestretch: '1.5'
output:
  pdf_document:
    toc: false
    number_sections: false
    keep-tex: true
geometry: margin=0.78in
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
fontsize: 12pt

---

>>>>

---
title: "Perceptions of Inequality and Meritocracy: Their Interplay in Shaping Preferences for Market Justice in Chile (2016-2023)"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
  pdf: 
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    number-sections: true
editor: source
link-citations: true
linestretch: 1.15       
mainfont: Times New Roman
fontsize: 12pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---
